Subsegmental language detection in Celtic language text

### 2014-05-09 codeswitch-cltw-2014/codeswitch.tex
subsections+
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52734 72bbbca6-d526-0410-a7d9-f06f51895060
+
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52735 72bbbca6-d526-0410-a7d9-f06f51895060

Alphabet n-gram approach -

@@

Code-Switch Chunking - \\

@@

Word based prediction -

@@

Word based Prediction with Character backoff -

  A better way to predict the spans of the sub-segments of the text is to include the two methods of word and character based techniques as described above. In case of the word being present in only one of the two monolingual word lists the classification is simple, but in case of a confusion as described in Word based prediction. above, a character bigram backoff was introduced to help us disambiguate the language label. This method works well because the earlier heuristic approach of just labelling the word with the label of the span which is expanding, would mean less code-switch detection and more shift towards baseline. \\

@@

Baseline \\

@@

Langid character bigram and trigram prediction - \\

>>>>

\subsection{Alphabet n-gram approach}
\label{alphan}

@@

\subsection{Code-Switch Chunking}
\label{cschunking}

@@

\subsection{Word based prediction}
\label{wbased}

@@

\subsection{Word based Prediction with Character backoff}
\label{wbasedbackoff}

  A better way to predict the spans of the sub-segments of the text is to include the two methods of word and character based techniques as described above. In case of the word being present in only one of the two monolingual word lists the classification is simple, but in case of a confusion as described in ~/ref{wbasedbackoff}. above, a character bigram backoff was introduced to help us disambiguate the language label. This method works well because the earlier heuristic approach of just labelling the word with the label of the span which is expanding, would mean less code-switch detection and more shift towards baseline. \\

@@

\subsection{Baseline}
\label{baseline}

@@

\subsection{Langid character bigram and trigram prediction}
\label{langidstuff}
